Simulation Modeling of Glycosylation Effects on Potassium Channels of Mouse Cardiomyocytes

### 2021-06-22 draft_plos.tex
Edit math commands

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the primary reason for heart transplantation; upward of 70\% of DCM cases are considered idiopathic. Our in-vitro experiments showed that reduced hybrid/complex N-glycosylation in mouse cardiomyocytes is linked with DCM. Further, we observed direct effects of reduced N-glycosylation on $\text{K}_{v}$ gating. However, it is difficult to rigorously determine the effects of glycosylation on $\text{K}_{v}$ activity, because there are multiple $\text{K}_{v}$ isoforms in cardiomyocytes. Due to complex functions of $\text{K}_{v}$ isoforms, only the sum of $\text{K}^{+}$ currents ($\text{I}_{Ksum}$) can be recorded experimentally and decomposed later using exponential fitting to estimate component currents such as $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$. However, such estimation cannot adequately describe glycosylation effects and $\text{K}_{v}$ mechanisms. Here, we propose to develop simulation models of $\text{K}_{v}$ kinetics in mouse ventricular myocytes and calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene (i.e., Mgat1KO). Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not directly observed in the in-vitro experiments. A novel calibration procedure is also proposed to tackle nonlinear and high-dimensionality challenges in simulation models. Experimental results show that, in the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower. The proposed approach has strong potential to couple simulation models with experimental data for gaining a better understanding of glycosylation effects on $\text{K}_{v}$ kinetics.

@@

Thus, we investigated the impact of reduced hybrid/complex N-glycosylation through the lens of electrophysiology. Electrophysiology refers to studies of electrical properties in scales from ion channels in cells to organ systems \cite{scanziani2009electrophysiology}. Electrical signaling in the heart has vital functions related to intra and extracellular communication, rhythmicity of heartbeats, and provides a driving force for contraction. The action potential (AP) is the net transmembrane potential varying over time which results from the composite activities of different ion channels \cite{grant2009cardiac}. Fig~\ref{fig1}-(a) shows the simulated AP of a mouse ventricular apex myocyte using models adopted from \cite{bondarenko2004computer}. The AP is the result of orchestrated activities of various ionic currents described in Fig-(b). Even small changes in VGIC function can contribute to aberrant AP waveform and/or conduction, leading to arrhythmias. As illustrated in Fig~\ref{fig2}, $\text{Na}^{+}$ channels ($\text{Na}_{v}$) are responsible for AP initiation, or the depolarization phase, $\text{Ca}^{2+}$ channels ($\text{Ca}_{v}$) drive the prolonged depolarization phase particularly in larger species (“plateau”), while several $\text{K}^{+}$ channel ($\text{K}_{v}$) isoforms are collectively responsible for AP deactivation, i.e., repolarization. Like most transmembrane proteins, VGICs are heavily glycosylated membrane proteins \cite{ednie2011modulation}. Studies have proven that glycosylation can affect VGIC function predominantly. For example, we reported that a saturating, electrostatic effect of negatively charged sialic acids, which are typically attached to the terminal of glycan branches, significantly altered cardiac electrical signaling \cite{ednie2013expression, ednie2015reduced}. Our recent studies observed aberrant electrical signaling, e.g., prolonged APs and abnormal early re-activations, in Mgat1KO ventricular apex myocytes \cite{ednie2019reduced, ednie2019reduced2}. These observations strongly support direct and disease-related effects of reduced N-glycosylation on VGIC gating and activity.

\begin{figure}[!ht]
    \centering
    \caption{Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$, $\text{I}_{Na}$, and $\text{I}_{CaL}$) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
    \label{fig1}
\end{figure}

@@

Although these in-vitro experiments showed changes in activities of ion channels, there are certain limitations that include: 1) \textit{Detailed ion channel kinetics are difficult to determine rigorously using in-vitro experiments alone}. From the electrophysiological experiment, pathological electrical signaling can be observed through measurements of APs at the whole-cell level and currents at the ion-channel level. However, it is difficult to relate, rigorously, the impacts of VGIC gating changes to the altered AP waveform/conduction and vice versa. 2) \textit{Segregating different $\text{K}^{+}$ currents ($\text{I}_{K}$) is difficult using whole-cell recording experimental techniques only}. $\text{I}_{Ksum}$ is the result of joint activity of multiple isoforms with each isoform producing a different, but slightly overlapping (in activation and inactivation voltages) component of the total $\text{K}^{+}$ current ($\text{I}_{Ksum}$) \cite{du2017} that contributes to various portions of AP repolarization. However, in-vitro experiments can only measure the sum of these component currents ($\text{I}_{Ksum}$) using whole-cell voltage-clamp protocols. Even pharmacologic separation of $\text{K}_{v}$ current types is difficult, as the specificity of drugs for a single current type is not ideal. Hence, component $\text{K}^{+}$ currents are usually estimated through multiple exponential fits of the decaying portion (due to channel inactivation) of the total $\text{K}^{+}$ current \cite{brunet2004heterogeneous}. Although the exponential function illustrates the shape of a component-current trace well, it cannot adequately describe kinetic dynamics of the current, nor fully and rigorously distinguish among currents produced by different $\text{K}_{v}$ isoforms because of their slightly overlapping voltage-dependence of gating. As $\text{K}_{v}$ have a critical function in repolarizing the cell, it is imperative to model and examine $\text{K}_{v}$ isoforms thoroughly.

Therefore, this paper presents simulation modeling of dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and further calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Specifically, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity, $\text{I}_{Kto}$ and $\text{I}_{Kslow}$, in mouse cardiomyocytes.  Fig~\ref{fig3} shows  major component $\text{K}^{+}$ currents, including $\text{I}_{Ksum}$, $\text{I}_{Kto}$, $\text{I}_{Kslow}$ and $\text{I}_{Kss}$. Key statistics of component currents, amplitudes, and inactivation rates ($\tau$'s) are measured from in-vitro experimental data with a 4.5 s voltage-clamp protocol (see details in Section III). The major contributions of this paper are summarized as follows.
\begin{itemize}
    \item Simulation models are integrated with in-vitro experiments to investigate the effects of reduced N-glycosylation on $\text{K}_{v}$ activity of mouse myocytes. Computer simulation helps demonstrate the voltage-gating mechanism and conductance kinetics that cannot be readily available through traditional exponential fitting. 
    \item A self-breeding Genetic Algorithm procedure is developed to calibrate simulation models of voltage-gated $\text{K}^{+}$ channel of mouse ventricular apex myocytes based on key characterisitcs and raw data obtained from in-vitro experiments.
    \item Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not observed in the in-vitro experiments. In the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower.
    \item Simulation modeling of cardiac myocytes is conducive to gain a better understanding of detailed $\text{K}_{v}$ kinetics, as well as how reduced glycosylation through ablation of Mgat1 gene impacts $\text{K}_{v}$ kinetics.
\end{itemize}

@@

In the literature, optimization procedures have been proposed to fit cardiomyocyte simulation models to electrophysiological experimental data. For example, $\text{Na}_{v}$ activity was coupled with in-vitro data of mouse cardiomyocyte using fractional factorial design and a Gaussian process model \cite{du2015statistical}. Fractional factorial designs were used to find significant control variables from the entire set of tuning parameters to reduce dimensionality. The Gaussian process model, which is computationally cheaper than the original $\text{Na}_{v}$ model, has served as a surrogate model to find optimal parameters. Characteristic curves such as steady-state activation (SSA), steady-state inactivation (SSI), and time constant of inactivation at different voltage were used to calculate goodness-of-fit as an objective function of optimization to minimize discrepancies with in-vitro experiment data. However, they are derived from current traces recorded during in-vitro experiments and may not always be available. For example, in our Mgat1KO data, currents were too small at early-activating voltages to reliably calculate the characteristic curves.

\subsection*{$\text{K}_{v}$ Isoforms}
The orchestrated activity of different $\text{K}_{v}$ isoforms produces multiple component currents, as illustrated in Fig~\ref{fig1}-(b) and Fig~\ref{fig3} However, it is difficult to rigorously delineate the multiple component $\text{K}^{+}$ currents through voltage-clamp experiments alone because only the sum of $\text{K}^{+}$ currents is measured and recorded. Thus, $\text{I}_{Ksum}$ is usually decomposed mathematically by fitting the peak and decaying portion of each component current trace with an exponential function \cite{brunet2004heterogeneous}. As given in Eq~\ref{eq1}, a standard exponential function has three parameters: amplitude ($\text{A}$), time constant ($\tau$), and constant offset value $\text{C}$. $t$ is time in millisecond. Amplitude refers to the value of the peak and $\tau$ to the time constant when current reduces by $e^{-1}$ (~63\%) of the peak.

\begin{figure}[!ht]
    \centering
    \caption{Example of $\text{K}^{+}$ current decomposition into three component currents. Each component $\text{K}^{+}$ current has different characteristics in terms of their peak and decaying phase.}
    \label{fig3}
\end{figure}

\begin{equation}
    \text{I} = \text{A}e^{-t/\tau} + \text{C}
    \label{eq1}
\end{equation}

In mouse ventricular myocytes, $\text{I}_{Ksum}$ has often been decomposed into three dominant currents, with one current having a high peak and decaying rapidly ($\text{I}_{Kto}$), a second current having a smaller peak and decaying slowly ($\text{I}_{Kslow}$), and the third current type being constant ($\text{I}_{Kss}$), so that a bi-exponential function with a constant component, as in Eq~\ref{eq2}, was used to separate different current components for 4.5-second protocols \cite{ednie2015reduced}. Fig~\ref{fig3} shows an example of the decomposition of $\text{I}_{Ksum}$ into three component currents. $\text{I}_{Kto}$ is a rapidly inactivating transient outward current that has a high peak at the very beginning of activation and rapid inactivation. $\text{I}_{Kslow}$, a delayed rectifier-type current, has a low peak and longer inactivation phase. $\text{I}_{Kss}$, a non-inactivating steady-state current, remains constant during the course of depolarization. In Eq~\ref{eq2}, $\text{A}_{Kto}$ and $\text{A}_{Kslow}$ are the amplitudes; $\tau_{Kto}$ and $\tau_{Kslow}$ are time constants of $\text{I}_{Kto}$ and $\text{I}_{Kslow}$, respectively. $\text{A}_{Kss}$ is the constant current $\text{I}_{Kss}$. Although bi-exponential fitting captures essential characteristics of three major component $\text{K}^{+}$ currents and describes the $\text{I}_{Ksum}$ waveform, it cannot provide detailed kinetic dynamics of $\text{K}_{v}$ isoforms \cite{plumlee2016calibrating}.

\begin{equation}
    \text{I}_{Ksum} = \text{A}_{Kto} e^{-t/\tau_{Kto}} + \text{A}_{Kslow} e^{-t/\tau_{Kslow}} + \text{A}_{Kss}
    \label{eq2}
\end{equation}

\section*{Methods}
% === III. METHODS ======================================================
% =======================================================================
In this study, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity in mouse cardiomyocytes. Coupling in-vitro data of $\text{K}_{v}$ with in-silico models has advantages that bi-exponential fitting cannot provide. For example, ionic currents, action potentials, and conductance can be determined more rigorously; and models allow for the simulation and prediction of glycosylation conditions that are not observed in the in-vitro experiment.

Specifically, this paper presents a new method that fits the simulation models directly to amplitudes and $\tau$'s, which are the most critical characteristics to describe component $\text{K}^{+}$ current traces. Eq~\ref{eq3} shows the objective function of the suggested optimization procedure, where $\hat{A_i}$ and $\hat{\tau_i}$ are estimations of amplitude and time constant from the simulation model. Potassium channels from mouse ventricular myocytes are modeled and parameterized based on partial differential equations. Then, full factorial designs are used to discover sensitive variables from the potential set of parameters. Further, a genetic algorithm-based heuristic optimization method is developed to calibrate the models to the data.

\begin{equation}
    \min (|\text{A}_i - \hat{\text{A}_i}| + |\tau_i - \hat{\tau_i}|), \ i \in \{Kto,\ Kslow\}
    \label{eq3}
\end{equation}

\subsection*{In-vitro Experimental Data}
Recently, we reported electrophysiological experiment data to investigate the impact of reduced hybrid/complex N-glycosylation on left ventricular cardiomyocyte activity, through deletion of the Mgat1 gene, which encodes a critical glycosyltransferase (GlcNAcT1) \cite{ednie2019reduced, ednie2019reduced2}. The detailed process of creation of Mgat1KO (Mgat1 Knock Out) strain, features of the cardiomyocyte-specific Mgat1KO strain, breeding, genotyping, and selection of wild type (WT) animals were previously described in \cite{ednie2019reduced2}. In our previous study of $\text{K}_{v}$ activities in the Mgat1KO \cite{ednie2019reduced}, cells of 12 to 20-week-old mice were used and numbers of observation for WT and Mgat1KO are 35 and 38 respectively.

As mentioned earlier, $\text{I}_{Ksum}$ was measured using whole-cell voltage clamp protocols. Cells were held at -70 mV and then depolarized by 10 mV voltage steps from -50 mV to 50 mV for 4.5 seconds. Note that this paper does not include the 25s depolarization, which often helps distinguish $\text{I}_{Kslow1}$ ($\text{K}_{v}1.5$ activity) and $\text{I}_{Kslow2}$ ($\text{K}_{v}2.1$ activity). Our ongoing experiments focus on voltage-clamp experiments on 25-second periods. The resulted data will be further studied and calibrated with simulation models in the future work.

>>>>

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package us`e within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

@@

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the primary reason for heart transplantation; upward of 70\% of DCM cases are considered idiopathic. Our in-vitro experiments showed that reduced hybrid/complex N-glycosylation in mouse cardiomyocytes is linked with DCM. Further, we observed direct effects of reduced N-glycosylation on K\textsubscript{v} gating. However, it is difficult to rigorously determine the effects of glycosylation on K\textsubscript{v} activity, because there are multiple K\textsubscript{v} isoforms in cardiomyocytes. Due to complex functions of K\textsubscript{v} isoforms, only the sum of K\textsuperscript{+} currents (I\textsubscript{Ksum}) can be recorded experimentally and decomposed later using exponential fitting to estimate component currents such as I\textsubscript{Kto}, I\textsubscript{Kslow}, I\textsubscript{Kss}. However, such estimation cannot adequately describe glycosylation effects and K\textsubscript{v} mechanisms. Here, we propose to develop simulation models of K\textsubscript{v} kinetics in mouse ventricular myocytes and calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene (i.e., Mgat1KO). Calibrated models facilitate the prediction of K\textsubscript{v} characteristics at different voltages that are not directly observed in the in-vitro experiments. A novel calibration procedure is also proposed to tackle nonlinear and high-dimensionality challenges in simulation models. Experimental results show that, in the Mgat1KO group, both I\textsubscript{Kto} and I\textsubscript{Kslow} densities are shown to be significantly reduced and the rate of I\textsubscript{Kslow} inactivation is much slower. The proposed approach has strong potential to couple simulation models with experimental data for gaining a better understanding of glycosylation effects on K\textsubscript{v} kinetics.

@@

Thus, we investigated the impact of reduced hybrid/complex N-glycosylation through the lens of electrophysiology. Electrophysiology refers to studies of electrical properties in scales from ion channels in cells to organ systems \cite{scanziani2009electrophysiology}. Electrical signaling in the heart has vital functions related to intra and extracellular communication, rhythmicity of heartbeats, and provides a driving force for contraction. The action potential (AP) is the net transmembrane potential varying over time which results from the composite activities of different ion channels \cite{grant2009cardiac}. Fig~\ref{fig1}-(a) shows the simulated AP of a mouse ventricular apex myocyte using models adopted from \cite{bondarenko2004computer}. The AP is the result of orchestrated activities of various ionic currents described in Fig-(b). Even small changes in VGIC function can contribute to aberrant AP waveform and/or conduction, leading to arrhythmias. As illustrated in Fig~\ref{fig2}, Na\textsuperscript{+} channels (Na\textsubscript{v}) are responsible for AP initiation, or the depolarization phase, Ca\textsuperscript{2+} channels (Ca\textsubscript{v}) drive the prolonged depolarization phase particularly in larger species (“plateau”), while several K\textsuperscript{+} channel (K\textsubscript{v}) isoforms are collectively responsible for AP deactivation, i.e., repolarization. Like most transmembrane proteins, VGICs are heavily glycosylated membrane proteins \cite{ednie2011modulation}. Studies have proven that glycosylation can affect VGIC function predominantly. For example, we reported that a saturating, electrostatic effect of negatively charged sialic acids, which are typically attached to the terminal of glycan branches, significantly altered cardiac electrical signaling \cite{ednie2013expression, ednie2015reduced}. Our recent studies observed aberrant electrical signaling, e.g., prolonged APs and abnormal early re-activations, in Mgat1KO ventricular apex myocytes \cite{ednie2019reduced, ednie2019reduced2}. These observations strongly support direct and disease-related effects of reduced N-glycosylation on VGIC gating and activity.

\begin{figure}[!ht]
    \centering
    \caption{Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., I\textsubscript{Kto}, I\textsubscript{Kslow}, I\textsubscript{Kss}, I\textsubscript{Na}, and I\textsubscript{CaL}) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
    \label{fig1}
\end{figure}

@@

Although these in-vitro experiments showed changes in activities of ion channels, there are certain limitations that include: 1) \textit{Detailed ion channel kinetics are difficult to determine rigorously using in-vitro experiments alone}. From the electrophysiological experiment, pathological electrical signaling can be observed through measurements of APs at the whole-cell level and currents at the ion-channel level. However, it is difficult to relate, rigorously, the impacts of VGIC gating changes to the altered AP waveform/conduction and vice versa. 2) \textit{Segregating different K\textsuperscript{+} currents (I\textsubscript{K}) is difficult using whole-cell recording experimental techniques only}. I\textsubscript{Ksum} is the result of joint activity of multiple isoforms with each isoform producing a different, but slightly overlapping (in activation and inactivation voltages) component of the total K\textsuperscript{+} current (I\textsubscript{Ksum}) \cite{du2017} that contributes to various portions of AP repolarization. However, in-vitro experiments can only measure the sum of these component currents (I\textsubscript{Ksum}) using whole-cell voltage-clamp protocols. Even pharmacologic separation of K\textsubscript{v} current types is difficult, as the specificity of drugs for a single current type is not ideal. Hence, component K\textsuperscript{+} currents are usually estimated through multiple exponential fits of the decaying portion (due to channel inactivation) of the total K\textsuperscript{+} current \cite{brunet2004heterogeneous}. Although the exponential function illustrates the shape of a component-current trace well, it cannot adequately describe kinetic dynamics of the current, nor fully and rigorously distinguish among currents produced by different K\textsubscript{v} isoforms because of their slightly overlapping voltage-dependence of gating. As K\textsubscript{v} have a critical function in repolarizing the cell, it is imperative to model and examine K\textsubscript{v} isoforms thoroughly.

Therefore, this paper presents simulation modeling of dominant K\textsuperscript{+} currents in mouse ventricular myocytes and further calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Specifically, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity, I\textsubscript{Kto} and I\textsubscript{Kslow}, in mouse cardiomyocytes.  Fig~\ref{fig3} shows  major component K\textsuperscript{+} currents, including I\textsubscript{Ksum}, I\textsubscript{Kto}, I\textsubscript{Kslow} and I\textsubscript{Kss}. Key statistics of component currents, amplitudes, and inactivation rates ($\tau$'s) are measured from in-vitro experimental data with a 4.5 s voltage-clamp protocol (see details in In-vitro Experimental Data Section in Methods). The major contributions of this paper are summarized as follows.
\begin{itemize}
    \item Simulation models are integrated with in-vitro experiments to investigate the effects of reduced N-glycosylation on K\textsubscript{v} activity of mouse myocytes. Computer simulation helps demonstrate the voltage-gating mechanism and conductance kinetics that cannot be readily available through traditional exponential fitting. 
    \item A self-breeding Genetic Algorithm procedure is developed to calibrate simulation models of voltage-gated K\textsuperscript{+} channel of mouse ventricular apex myocytes based on key characterisitcs and raw data obtained from in-vitro experiments.
    \item Calibrated models facilitate the prediction of K\textsubscript{v} characteristics at different voltages that are not observed in the in-vitro experiments. In the Mgat1KO group, both I\textsubscript{Kto} and I\textsubscript{Kslow} densities are shown to be significantly reduced and the rate of I\textsubscript{Kslow} inactivation is much slower.
    \item Simulation modeling of cardiac myocytes is conducive to gain a better understanding of detailed K\textsubscript{v} kinetics, as well as how reduced glycosylation through ablation of Mgat1 gene impacts K\textsubscript{v} kinetics.
\end{itemize}

@@

In the literature, optimization procedures have been proposed to fit cardiomyocyte simulation models to electrophysiological experimental data. For example, Na\textsubscript{v} activity was coupled with in-vitro data of mouse cardiomyocyte using fractional factorial design and a Gaussian process model \cite{du2015statistical}. Fractional factorial designs were used to find significant control variables from the entire set of tuning parameters to reduce dimensionality. The Gaussian process model, which is computationally cheaper than the original Na\textsubscript{v} model, has served as a surrogate model to find optimal parameters. Characteristic curves such as steady-state activation (SSA), steady-state inactivation (SSI), and time constant of inactivation at different voltage were used to calculate goodness-of-fit as an objective function of optimization to minimize discrepancies with in-vitro experiment data. However, they are derived from current traces recorded during in-vitro experiments and may not always be available. For example, in our Mgat1KO data, currents were too small at early-activating voltages to reliably calculate the characteristic curves.

\subsection*{K\textsubscript{v} Isoforms}
The orchestrated activity of different K\textsubscript{v} isoforms produces multiple component currents, as illustrated in Fig~\ref{fig1}-(b) and Fig~\ref{fig3} However, it is difficult to rigorously delineate the multiple component K\textsuperscript{+} currents through voltage-clamp experiments alone because only the sum of K\textsuperscript{+} currents is measured and recorded. Thus, I\textsubscript{Ksum} is usually decomposed mathematically by fitting the peak and decaying portion of each component current trace with an exponential function \cite{brunet2004heterogeneous}. As given in Eq~\ref{eq1}, a standard exponential function has three parameters: amplitude ($\mathrm{A}$), time constant ($\tau$), and constant offset value ($\mathrm{C}$). $t$ is time in millisecond. Amplitude refers to the value of the peak and $\tau$ to the time constant when current reduces by $e^{-1}$ (~63\%) of the peak.

\begin{figure}[!ht]
    \centering
    \caption{Example of K\textsuperscript{+} current decomposition into three component currents. Each component K\textsuperscript{+} current has different characteristics in terms of their peak and decaying phase.}
    \label{fig3}
\end{figure}

\begin{equation}
    \mathrm{I} = \mathrm{A}e^{-t/\tau} + \mathrm{C}
    \label{eq1}
\end{equation}

In mouse ventricular myocytes, I\textsubscript{Ksum} has often been decomposed into three dominant currents, with one current having a high peak and decaying rapidly (I\textsubscript{Kto}), a second current having a smaller peak and decaying slowly (I\textsubscript{Kslow}), and the third current type being constant (I\textsubscript{Kss}), so that a bi-exponential function with a constant component, as in Eq~\ref{eq2}, was used to separate different current components for 4.5-second protocols \cite{ednie2015reduced}. Fig~\ref{fig3} shows an example of the decomposition of I\textsubscript{Ksum} into three component currents. I\textsubscript{Kto} is a rapidly inactivating transient outward current that has a high peak at the very beginning of activation and rapid inactivation. I\textsubscript{Kslow}, a delayed rectifier-type current, has a low peak and longer inactivation phase. I\textsubscript{Kss}, a non-inactivating steady-state current, remains constant during the course of depolarization. In Eq~\ref{eq2}, $\mathrm{A}_{Kto}$ and $\mathrm{A}_{Kslow}$ are the amplitudes; $\tau_{Kto}$ and $\tau_{Kslow}$ are time constants of I\textsubscript{Kto} and I\textsubscript{Kslow}, respectively. $\mathrm{A}_{Kss}$ is the constant current I\textsubscript{Kss}. Although bi-exponential fitting captures essential characteristics of three major component K\textsuperscript{+} currents and describes the I\textsubscript{Ksum} waveform, it cannot provide detailed kinetic dynamics of K\textsubscript{v} isoforms \cite{plumlee2016calibrating}.

\begin{equation}
    \mathrm{I}_{\mathrm{Ksum}} = \mathrm{A}_{Kto} e^{-t/\tau_{Kto}} + \mathrm{A}_{Kslow} e^{-t/\tau_{Kslow}} + \mathrm{A}_{Kss}
    \label{eq2}
\end{equation}

\section*{Methods}
% === III. METHODS ======================================================
% =======================================================================
In this study, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity in mouse cardiomyocytes. Coupling in-vitro data of K\textsubscript{v} with in-silico models has advantages that bi-exponential fitting cannot provide. For example, ionic currents, action potentials, and conductance can be determined more rigorously; and models allow for the simulation and prediction of glycosylation conditions that are not observed in the in-vitro experiment.

Specifically, this paper presents a new method that fits the simulation models directly to amplitudes and $\tau$'s, which are the most critical characteristics to describe component K\textsuperscript{+} current traces. Eq~\ref{eq3} shows the objective function of the suggested optimization procedure, where $\hat{A_i}$ and $\hat{\tau_i}$ are estimations of amplitude and time constant from the simulation model. Potassium channels from mouse ventricular myocytes are modeled and parameterized based on partial differential equations. Then, full factorial designs are used to discover sensitive variables from the potential set of parameters. Further, a genetic algorithm-based heuristic optimization method is developed to calibrate the models to the data.

\begin{equation}
    \min (|\mathrm{A}_i - \hat{\mathrm{A}_i}| + |\tau_i - \hat{\tau_i}|), \ i \in \{\mathrm{Kto},\ \mathrm{Kslow}\}
    \label{eq3}
\end{equation}

\subsection*{In-vitro Experimental Data}
Recently, we reported electrophysiological experiment data to investigate the impact of reduced hybrid/complex N-glycosylation on left ventricular cardiomyocyte activity, through deletion of the Mgat1 gene, which encodes a critical glycosyltransferase (GlcNAcT1) \cite{ednie2019reduced, ednie2019reduced2}. The detailed process of creation of Mgat1KO (Mgat1 Knock Out) strain, features of the cardiomyocyte-specific Mgat1KO strain, breeding, genotyping, and selection of wild type (WT) animals were previously described in \cite{ednie2019reduced2}. In our previous study of K\textsubscript{v} activities in the Mgat1KO \cite{ednie2019reduced}, cells of 12 to 20-week-old mice were used and numbers of observation for WT and Mgat1KO are 35 and 38 respectively.

As mentioned earlier, I\textsubscript{Ksum} was measured using whole-cell voltage clamp protocols. Cells were held at -70 mV and then depolarized by 10 mV voltage steps from -50 mV to 50 mV for 4.5 seconds. Note that this paper does not include the 25s depolarization, which often helps distinguish I\textsubscript{Kslow1} (K\textsubscript{v}1.5 activity) and I\textsubscript{Kslow2} (K\textsubscript{v}2.1 activity). Our ongoing experiments focus on voltage-clamp experiments on 25-second periods. The resulted data will be further studied and calibrated with simulation models in the future work.

\begin{figure}[!ht]
    \centering
    \caption{In-vitro experimental results, adopted from \cite{ednie2019reduced}, of averages and error bars of (a) the peaks and constant current, and (b) inactivation time constant. As reported in \cite{ednie2019reduced}, significant differences between WT and Mgat1KO at $p \leq 0.05$ are indicated by an *. ($n=35$ for WT and $n=38$ for Mgat1KO).}
    \label{fig4}
\end{figure}
